%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Sr. Manager of Operations Research - Lead development of decision support tools for railroads}     % Job title
{CSX Transportation Inc.}                % Organization
{Jacksonville, FL}                       % Location
{Apr 2016 - Present}                     % Date(s)
{
    \begin{cvitems}                          
        \item {
\textbf{Line-of-road (LOR) Train Planner} 
{(Team leader \& major developer) }  \\ 
LOR Train Planner is a web-based tool (\textit{Django + JavaScript}) to help optimize road-train planning. The core part is a heuristic-based algorithm that does the meet-and-pass planning to guide trains through a division. Data-mining models (\textit{SVR, Decision Tree}) are embedded to estimate train speeds with high accuracy. The tool are widely used in CSX -- it helps service planners re-design and evaluate new plans; Engineering teams use it to find proper time windows for maintenance; Network operation teams use it to do performance / capacity / impact analysis, etc. \textit{Python} was selected to implement the tool and \textit{JIRA + GIT} was utilized to manage the development process and facilitate team collaboration.            
        }
    \end{cvitems}% Description(s) of tasks/responsibilities  
}

%---------------------------------------------------------
\cventry
{Manager of Operations Research - Developed and managed multiple OR projects}         % Job title
{}                                       % Organization
{}                                       % Location
{Mar 2012 - Mar 2016}                    % Date(s)
{                                        % Description(s) of tasks/responsibilities
    \begin{cvitems}  
        \item {
\textbf{Line-of-road (LOR) Emulator} 
{(Sole developer)}  \\
LOR Emulator is a visualization tool which can animate train movements (historical or planned) on a GIS view. It detects slow-moving or long-dwelled trains and and highlights them with colorful bubbles, so that users can easily identify the bottleneck of rail network. The tool was developed using \textit{Java + JavaScript (jQuery, D3)}, and has been used to create a video for the executive team and the board of CSX to understand how congestion happened on the northern tier corridor in 2014, and received a high appreciation (achieved CSX Spotlight award).
		}
        \item {
\textbf{Nashville Locomotive Workshop Simulation}
{(Sole modeler) } \\
Nashville locomotive workshop model (\textit{AnyLogic}) is a simulation model to help mechanical department evaluate the capacity on throughput for different designs of new locomotive workshop. The model shows 3D animation of train movements from starting at service center till ending at ready tracks, and provides charts to show performance measures (throughput and dwell times).        
        }
        \item {
\textbf{Hump Yard Simulation System (HYSS)}
{(Project manager \& developer)}  \\
HYSS is a web-based simulation system consisting of six hump yard models. It simulates yard processes and provides strategic and tactical decision support, such as track utilization planning and right-sizing of yard resources. My major duties include:      
        }
        \begin{itemize}
            \item  Manage project progress, reviewed and maintained source codes delivered by vendor;
            \item  Created a suit of statistical matrices to validate the models prior to acceptance;
            \item  Developed "HYSS input generator" (\textit{MS C\# + Access + SQL Server}) to speed up input data preparation (compress the preparation time from six weeks to three days).
        \end{itemize}          
    \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Intern}          % Job title
{ANSYS Inc.}             % Organization
{Canonsburg, PA}                       % Location
{May 2006 - Sep 2006}                  % Date(s)
{
    \begin{cvitems}                          
        \item {
Designed and developed the user interface (UI) and pre-processor module using \textit{Visual C++} with \textit{QT}. The pre-processor formats the input data using XML, generates command flow scripts and outputs the scripts into files. The script files are then used as the input for the finite element analysis module.
		}
        \item {
Tested and benchmarked the multi-physics coupling modules of new version ANSYS® (v11.0).
		}        
    \end{cvitems}% Description(s) of tasks/responsibilities  
}

%---------------------------------------------------------
\cventry
{Research/Teaching Assistant}          % Job title
{University of Pittsburgh}             % Organization
{Pittsburgh, PA}                       % Location
{Sep 2005 - Feb 2012}                  % Date(s)
{
    \begin{cvitems}                          
        \item {
Developed methodology to efficiently identify the best response strategies for PEMA (Pennsylvania Emergency Management Agency, funding provider) by integrating agent-based simulation (\textit{Java + RePast}) with advanced statistical selection algorithm (\textit{R}).
		}
        \item {
Taught/assisted undergraduate courses: IE-1083: Simulation with Arena (Arena\markright, 40+ students, 2011), IE-1051: Computer Aided Design (SolidWorks\markright, 30+ students, 2005).
		}        
    \end{cvitems}% Description(s) of tasks/responsibilities  
}

%---------------------------------------------------------
\cventry
{Software Engineer - Developed multiple J2EE-based web-applications}                   % Job title
{COFCO Group}                         % Organization
{Beijing, China}                      % Location
{Jul 2003 -- Jul 2005}                % Date(s)
{
    \begin{cvitems}                          
        \item {
\textbf{Agricultural information subscribing platform} -- provided agricultural information via cellphone short-messages to its subscribers (collaborative project between COFCO, CCTV-7 and China National Radio).
		}          
        \item {
\textbf{Employee Satisfaction Survey System for HR of COFCO} -- employed in headquarters and two subsidiaries of COFCO (~500 employees involved) in 2005 and 2006. % (\textbf{J2EE/JSP/Servlet + Struts + Hibernate + XML + SQL})
		}        
    \end{cvitems}  % Description(s) of tasks/responsibilities  
}
%---------------------------------------------------------
\end{cventries}
