%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Contributions}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Selected Papers (first-author)}      % Role
{}                            % Event
{}                                         % Location
{}                                         % Date(s)
{
\begin{cvitems} % Description(s)
    \item {
\textbf{Yu Wang}, K. Louis Luangkesorn, and Larry Shuman. "Modeling emergency medical response to a mass casualty incident using agent based simulation." \textit{Socio-Economic Planning Sciences} Vol.46, No.4, p281-290, 2012
	}
    \item {
\textbf{Yu Wang}, Louis Luangkesorn, and Larry J. Shuman. "Best-subset selection procedure." In 
\textit{Simulation Conference (WSC), Proceedings of the 2011 Winter}, p4310-4318, IEEE, 2011.
	}
	\item {
\textbf{Yu Wang}, Haiyan Zhao, Su Wu, et al. "Establishment of segmented moving double ellipsoid heat source model in electron beam welding numerical simulation." 
\textit{Chinese Journal of Mechanical Engineering}, Vol.40, No.2, p165-169, 2004
	}
    \item {
\textbf{Yu Wang}, Su Wu, Haiyan Zhao, et al. "An investigation on the shape parameters of double ellipsoid heat source model in numerical simulation of high energy beam welding." 
\textit{Transactions of the China Welding Institution}, Vol.24, No.2, p67-70, 2003
	}	
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Presentations on INFORMS Annual Meetings}      % Role
{}                            % Event
{}                                         % Location
{}                                         % Date(s)
{
\begin{cvitems} % Description(s)
    \item {
CSX Line-of-Road Simulation. \textit{Nashville, TN}, 2016
	}
    \item {
Development and Application of Line-of-road Emulator Tool in CSX. \textit{Philadelphia, PA}, 2015
	}
	\item {
Predict Congestion Status of a Hump Yard using Data-mining. \textit{Minneapolis, MN}, 2013
	}
    \item {
An Agent-based Simulation for Emergency Response Policy Evaluation \& Selection. \textit{Austin, TX}, 2010
	}	
\end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
